### 2015-02-28 icfp15-servo/browsers.tex
the identifier `flow tree` was used before it was declared

After constructing the DOM and determining the set of styles defined in the Cascading Style Sheets (CSS) that has
been loaded, those styles are applied to the DOM and a new flow tree that represents the elements is created.
This process can create many more flows than previously existed in the DOM --- for example, when a list item is
styled to have an associated counter glyph.

@@

That tree of elements, called the \emph{flow tree} in Servo, is then processed
to produce a set of \emph{display list} items.  These list items are the
actual graphical elements, text runs, etc. in their final on-screen positions.
The order in which these elements are displayed is well-defined by the
standard\footnote{\url{http://www.w3.org/TR/CSS21/zindex.html#painting-order}}.

>>>>

After constructing the DOM and determining the set of styles defined in the Cascading Style Sheets (CSS) that has
been loaded, those styles are applied to the DOM and a new tree that represents the elements is created. In Servo, we call this the \emph{flow tree}.
This process can create many more flows than previously existed in the DOM --- for example, when a list item is
styled to have an associated counter glyph.

@@

The flow tree is then processed
to produce a set of \emph{display list} items.  These list items are the
actual graphical elements, text runs, etc. in their final on-screen positions.
The order in which these elements are displayed is well-defined by the
standard\footnote{\url{http://www.w3.org/TR/CSS21/zindex.html#painting-order}}.
